Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-01 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
Slight revision with some comments

Interactive evolutionary computation (IEC) systems are, in general, methods
of evolutionary computation whose fitness evaluations are performed by humans 
within an interactive system \cite{eiben2015interactive}.  Human evaluation 
is needed because the fitness function is not known and the result
of optimization should fit certain human need. Usually human preference is
needed to evaluate subjective characteristics like visual appeal or 
attractiveness \cite{biomorphs}, but in other cases human behavior is 

@@

Using a volunteer based system  
brings other issues \cite{sarmenta2001volunteer,web:BOINC}, 

@@

In evolutionary computation algorithms are data driven, as it is important to keep data about the 

@@

For example, in a C-IEC application, fitness assignment depend on the actions of a social network of users. 

@@

The remainder of this paper is organized as follows.
Section \ref{sec:interactive} presents related work on the topic 
of Interactive Evolution.
Then, Section \ref{sec:e} presents the Model of Human Interactions in Collaborative Interactive 
 Evolutionary Computation which 
the main proposal of this work. An implementation using the EvoSpace-Interactive  framework is detailed in Section \ref{sec:HCF}.
The case studies  and results are presented in Section \ref{sec:experiments}.
Finally, a concluding remarks are provided in Section \ref{sec:conclusions}.

@@

\begin{acks}
  The authors would like to thank Dr. Yuhua Li for providing the
  matlab code of  the \textit{BEPS} method.

  The authors would also like to thank the anonymous referees for
  their valuable comments and helpful suggestions. The work is
  supported by the \grantsponsor{GS501100001809}{National Natural
    Science Foundation of
    China}{http://dx.doi.org/10.13039/501100001809} under Grant
  No.:~\grantnum{GS501100001809}{61273304}
  and~\grantnum[http://www.nnsf.cn/youngscientsts]{GS501100001809}{Young
    Scientsts' Support Program}.

>>>>

Interactive evolutionary computation (IEC) systems are, in general, evolutionary methods
whose fitness evaluations are performed by humans through an
interactive system \cite{eiben2015interactive}. They are usually
applied in problems where the fitness function is not known  or simply
does not exist, and the result
of optimization should fit certain human and possibly aesthetic
need. That is why their use case includes the evolution of objects
with subjective characteristics such visual appeal or 
attractiveness \cite{biomorphs} as well as others where human behavior is 

@@

Using a volunteer based system raises other issues \cite{sarmenta2001volunteer,web:BOINC}, 

@@

% It's the tuning of the algorithm which is data driven, not the
% algorithm itself, right? - JJ
In evolutionary computation algorithms are data driven since it is important to keep data about the 

@@

For example, in a C-IEC application, fitness assignment depend on the
actions of a social network of users. 

@@

The rest of this paper is organized as follows.
Section \ref{sec:interactive} presents related work on the topic 
of Interactive Evolution.
Then, Section \ref{sec:e} presents the Model of Human Interactions in Collaborative Interactive 
 Evolutionary Computation which 
the main proposal of this work. An implementation using the EvoSpace-Interactive  framework is detailed in Section \ref{sec:HCF}.
The case studies  and results are presented in Section \ref{sec:experiments}.
Finally, a concluding remarks are provided in Section \ref{sec:conclusions}.

@@

\begin{acks}
  % The authors would like to thank Dr. Yuhua Li for providing the
  % matlab code of  the \textit{BEPS} method.

  % The authors would also like to thank the anonymous referees for
  % their valuable comments and helpful suggestions. The work is
  % supported by the \grantsponsor{GS501100001809}{National Natural
  %   Science Foundation of
  %   China}{http://dx.doi.org/10.13039/501100001809} under Grant
  % No.:~\grantnum{GS501100001809}{61273304}
  % and~\grantnum[http://www.nnsf.cn/youngscientsts]{GS501100001809}{Young
  %   Scientsts' Support Program}.
